What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2022-12-31 paper/main.tex
added table of LTL formulas and some of the formulas

\newcommand{\tool}{\texttt{ltl2timeline}}

@@

%Purpose & \# formulas & source

>>>>

\newcommand{\tool}{\hspace{0.1cm}\texttt{ltl2timeline}\hspace{0.1cm}}

@@

\noindent
\begin{tabular}{p{3.6in}|c|c}
  \hline
  Purpose & \# formulas & Source \\
  \hline
  Design space for NASA's AAC (Automated Airspace Concept) & 20,250 & \cite{GCMTR16} \\
  \hline
  Safety specificatons for Boeing's AIR6110 wheel brake system & & \cite{BCFJKPRT15} \\
  \hline
  Requirements for model checking NASA's AAC high-level architecture & 6 & \cite{ZR14} \\
  \hline
  Real formulas collected from all publicly-available, pre-2011 case studies &  & \cite{RV11} \\
  \hline
\end{tabular}
